### 2025-05-29 manuscript/titlepage.qmd
fix repo

#### **Adversity is associated with lower general processing speed rather than specific executive functioning abilities**

@@

Stefan Vermeent served as lead for conceptualization, data curation, methodology, formal analysis, and writing the original draft. Anna-Lena Schubert served in a supporting role for conceptualization, formal analysis, methodology, and writing-review and editing. Willem E. Frankenhuis served in a supporting role for conceptualization, methodology, supervision, funding acquisition, and writing-review and editing.

The preregistration, analysis scripts, and study materials are available on the article's Github repository ([https://stefanvermeent.github.io/liss_ef_2024/](https://stefanvermeent.github.io/liss_ef_2024/)).
In this paper, we make use of data from the LISS panel (Longitudinal Internet studies for the Social Sciences) managed by the non-profit research institute Centerdata (Tilburg University, the Netherlands). 
All datasets are available to researchers in the LISS data archive, after signing a data use agreement ([https://www.dataarchive.lissdata.nl/study-units/view/1](https://www.dataarchive.lissdata.nl/study-units/view/1)).

Correspondence concerning this article should be addressed to Stefan Vermeent, Department of Psychology, Utrecht University, Heidelberglaan 1, 3584 CS Utrecht, The Netherlands. Email: p.c.s.vermeent@gmail.com / p.c.s.vermeent@uu.nl.

We have no conflict of interest to disclose.

**word count:** 9573

>>>>

#### **Adversity is associated with lower general processing speed rather than executive functioning**

@@

This study was approved by the Ethics Review Board of the Faculty of Social & Behavioural Sciences of Utrecht University (FETC20-490) and the Ethics committee for research in the Sciences and Life Sciences of the University of Amsterdam (FNWI-41_2023).

All scripts and materials needed to reproduce the findings are available on the article's Github repository ([https://stefanvermeent.github.io/liss_ef_2024/](https://stefanvermeent.github.io/liss_ef_2024/)).
In this paper, we make use of data from the LISS panel (Longitudinal Internet studies for the Social Sciences) managed by the non-profit research institute Centerdata (Tilburg University, the Netherlands). 
All datasets are available in the LISS data archive ([https://www.dataarchive.lissdata.nl/study-units/view/1](https://www.dataarchive.lissdata.nl/study-units/view/1)). 
Researchers who want to access the data are required to sign a statement confirming that information about individual persons, households, etc., will not be released to others (go to [https://statements.centerdata.nl](https://statements.centerdata.nl) for more information).
The data and ideas in this manuscript were not presented elsewhere.

SV served as lead for conceptualization, formal analysis, funding acquisition, investigation, methodology, and writing - original draft.
AS served in a supporting role for supervision, conceptualization, methodology, formal analysis, and writing - review & editing.
WF served as lead for supervision, and in a supporting role for conceptualization, methodology, formal analysis, and writing - review & editing.

The authors declare no conflicts of interest.

Correspondence concerning this article should be addressed to Stefan Vermeent, Evolutionary and Population Biology, Institute for Biodiversity and Ecosystem Dynamics, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands. Email: p.c.s.vermeent@gmail.com.

**word count:** 10266

### 2025-05-29 supplement/supplement.qmd
fix repo

load("../analysis_objects/task_reliability.RData")
load("../analysis_objects/hddm_model_fit")
load("../analysis_objects/env_effects.RData")
load("../analysis_objects/iv_histograms.RData")
load("../analysis_objects/confounder_coefficients.RData")
load("../analysis_objects/ddm_correlations.RData")

@@

@@

>>>>

load("../analysis_objects/task_reliability.RData")
load("../analysis_objects/hddm_model_fit")
load("../analysis_objects/env_effects.RData")
load("../analysis_objects/iv_histograms.RData")
load("../analysis_objects/confounder_coefficients.RData")
load("../analysis_objects/ddm_correlations.RData")
load("../analysis_objects/ddm_histograms.RData")

@@

## Priors and model settings

We drew individual-level DDM parameters from normal distributions, separately for each condition (except for the Posner task, which only contained one condition). The normal distributions were truncated based on reasonable parameter ranges (between -10 and 10 for drift rates, between 0.1 and 5 for boundary separation, and between 0.0001 and 1 for non-decision time).
The normal distributions were given uninformative priors.

@@

## Distributions of DDM parameters

Figures S12-S14 present histograms of individual estimates of the three DDM parameters.
With a few exceptions (particularly in non-decision times), the DDM parameters were (approximately) normally distributed.

```{r}
#| label: FigureS12
#| fig-width: 6.5
#| fig-height: 8
#| dpi: 600
#| out-width: 6in
#| fig-cap: | 
#|   **Figure S12.** Distribution of drift rates.
hist_v
```

```{r}
#| label: FigureS13
#| fig-width: 6.5
#| fig-height: 8
#| dpi: 600
#| out-width: 6in
#| fig-cap: | 
#|   **Figure S12.** Distribution of boundary separations.
hist_a
```

```{r}
#| label: FigureS14
#| fig-width: 6.5
#| fig-height: 8
#| dpi: 600
#| out-width: 6in
#| fig-cap: | 
#|   **Figure S14.** Distribution of non-decision times.
hist_t
```
